CTest Integration of Sikuli Automated GUI Testing

### 2011-06-21 Documentation/Article.tex
submitted version

\begin{abstract}
\noindent
In order to test our software GoFigure2~\cite{GoFigure2:Website} (for the
visualization and the processing of extremely large $3D+t$ microscopy images),
we utilized the visual programming technology Sikuli~\cite{Sikuli:Website} to
automate our GUI testing. We then integrated these Sikuli tests into CTest and
used CDash to report the results on a dashboard with the view to test our
software automatically every night and detect bugs as soon as they occur.  Our
rate of releases more than doubled as a result.
\end{abstract}

>>>>

\begin{abstract}
\noindent
In order to test our software GoFigure2~\cite{GoFigure2:Website} for the
visualization and the processing of extremely large $3D+t$ microscopy images,
we utilized the visual programming technology Sikuli~\cite{Sikuli:Website} to
automate our GUI testing. We then integrated these Sikuli tests into CTest and
used CDash to report the results on a dashboard with the view to test our
software automatically every night and detect bugs as soon as they occur.  Our
rate of releases more than doubled as a result.\\

\noindent Source code and examples are available
here:~\url{https://github.com/gofigure2/SikuliCTest}
\end{abstract}
